A Comparison of Parallel Graph Processing Implementations

### 2017-05-15 papers/publication/paper-pollard.tex
efficiency text fix

%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
%source vertex: 55713
%num. threads: 64
%Starting file read of /home/users/spollard/graphalytics/graphalytics-platforms-graphmat/intermediate/dota-league.e_weight..mtx
%Got graph with m=61170  n=61170 nnz=101740626
%Finished file read of /home/users/spollard/graphalytics/graphalytics-platforms-graphmat/intermediate/dota-league.e_weight..mtx, time: 0.94948
%Finished setting ids, time: 0.077502
%Starting sort
%Finished sort, time: 0.767248
%Finished setting edge pointers, time: 0.00017
%Starting build_dcsc
%Finished build_dcsc, time: 0.162558
%Finished setting ids, time: 0.07698
%Starting sort
%Finished sort, time: 1.20438
%Finished setting edge pointers, time: 0.000169
%Starting build_dcsc
%Finished build_dcsc, time: 0.156858
%Completed reading A from memory in 2.522761 seconds.
%Completed reading A from file in 3.481659 seconds.
%Completed 19 iterations
%Timing results:
%- load graph: 3.48167 sec
%- initialize engine: 3.60012e-05 sec
%- run algorithm: 0.168526 sec
%- print output: 0.105846 sec
%- deinitialize engine: 6.00815e-05 sec
%03:17:45.114 [INFO ] Benchmarked algorithm "Single source shortest paths" on graph "dota-league".
%03:17:45.114 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" succeed.
%03:17:45.114 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 3830 ms.
With a plugin to Graphalytics called Granula~\cite{Ngai:2015:Granula}, one can explicitly specify a performance model to analyze specific execution behavior such as the amount of communication or runtime of particular kernels of execution. This requires in-depth knowledge of the source code and execution model in addition to expertise with the Granula API but allows detailed performance analysis and automatic execution and compilation of performance results.\footnote{An example of Granula can be seen at \url{https://github.com/tudelft-atlarge/graphalytics-platforms-graphx/tree/master/granula-model-graphx}}.

@@

We analyze the performance of the algorithms described in Sec.~\ref{sec:algs} in terms of execution time, scalability over multiple threads, and power and energy consumption. All figures except those measuring scalability (Fig.~\ref{fig:bfs-scaling}) use 32 threads.

@@

We define the parallel efficiency as $T_1 / (n T_n)$ where $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ is the time for $n$ threads. Ideal efficiency is defined as $T_n = T_1/n$ and is the horizontal line near the top of Fig.~\ref{fig:bfs-efficiency}. 
\begin{figure}[htb]
	\centering
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss20.pdf}
	\caption{Parallel efficiency for a scale-20 graph. GraphBIG dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time with $n$ threads.}
	\label{fig:bfs-efficiency}
\end{figure}

>>>>

%We use GraphMat, the single source shortest paths algorithm, the dota-league dataset from the Game Trace Archive\cite{Guo:2012:GTA}, and the default settings as an example here.
%source vertex: 55713
%num. threads: 64
%Starting file read of /home/users/spollard/graphalytics/graphalytics-platforms-graphmat/intermediate/dota-league.e_weight..mtx
%Got graph with m=61170  n=61170 nnz=101740626
%Finished file read of /home/users/spollard/graphalytics/graphalytics-platforms-graphmat/intermediate/dota-league.e_weight..mtx, time: 0.94948
%Finished setting ids, time: 0.077502
%Starting sort
%Finished sort, time: 0.767248
%Finished setting edge pointers, time: 0.00017
%Starting build_dcsc
%Finished build_dcsc, time: 0.162558
%Finished setting ids, time: 0.07698
%Starting sort
%Finished sort, time: 1.20438
%Finished setting edge pointers, time: 0.000169
%Starting build_dcsc
%Finished build_dcsc, time: 0.156858
%Completed reading A from memory in 2.522761 seconds.
%Completed reading A from file in 3.481659 seconds.
%Completed 19 iterations
%Timing results:
%- load graph: 3.48167 sec
%- initialize engine: 3.60012e-05 sec
%- run algorithm: 0.168526 sec
%- print output: 0.105846 sec
%- deinitialize engine: 6.00815e-05 sec
%03:17:45.114 [INFO ] Benchmarked algorithm "Single source shortest paths" on graph "dota-league".
%03:17:45.114 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" succeed.
%03:17:45.114 [INFO ] Benchmarking algorithm "Single source shortest paths" on graph "dota-league" took 3830 ms.
With a plugin to Graphalytics called Granula~\cite{Ngai:2015:Granula}, one can explicitly specify a performance model to analyze specific execution behavior such as the amount of communication or runtime of particular kernels of execution. This requires in-depth knowledge of the source code and execution model in addition to expertise with the Granula API but allows detailed performance analysis and automatic execution and compilation of performance results.\footnote{An example of Granula can be seen at \url{http://bit.ly/granula-example}}.
%\url{https://github.com/tudelft-atlarge/graphalytics-platforms-graphx/tree/master/granula-model-graphx}}.

@@

We analyze the performance of the algorithms described in Sec.~\ref{sec:algs} in terms of execution time, scalability over multiple threads, and power and energy consumption. All figures except those measuring scalability (Figs.~\ref{fig:bfs-speedup} and~\ref{fig:bfs-efficiency}) use 32 threads.

@@

Figure~\ref{fig:bfs-efficiency} shows the parallel efficiency,  $T_1 / (nT_n)$ for different implementations of BFS. Ideal efficiency is defined as $T_n = T_1/n$ and is the horizontal line near the top of Fig.~\ref{fig:bfs-efficiency}. 
\begin{figure}[htb]
	\centering
		\includegraphics[width=\linewidth, trim=0 18pt 18pt 12pt, clip]{graphics/bfs_ss20.pdf}
	\caption{Parallel efficiency for a scale-20 graph. GraphBIG dips below 1 because it is slower for $2$ threads than for 1. $T_1$ is the serial time, $n$ is the number of threads, and $T_n$ time with $n$ threads.}
	\label{fig:bfs-efficiency}
\end{figure}
